---
title: "Experimental"
author: "Ruben Lopez"
date: "12/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# renv workflow
```{r}
renv::snapshot()
# renv::restore()
```

```{r}
# devtools::install_github("rjlopez2/AnlysisOfWaves")

pacman::p_load(shiny, tidyverse, plotly, 
               DT, shinythemes, shinyFiles, fs, 
               usethis, devtools, ijtiff, AnlysisOfWaves,
               plotly, furrr)

```

```{r}
# usethis::use_github() # use this to set the github repository after project is been created locally.

```

# Reading a linescan image in tif format and plotting profile

```{r}
path_to_file <- "~/Desktop/new_intac_cell_repre_ls/CPVT/20190117 L1 CS3 Cell A0002_BG.tif"
path_to_file2 <- "/Volumes/RUBEN FILES/Ruben/Work/GroupNiggli/Confocal/2021/SR_exepriments/211214/CPVT-HET/P2/CS1"

```


```{r}

AnlysisOfWaves::make_profile_func(path_to_file) %>% 
  head

read_tags(path_to_file, frames = "all")
```

# create df from profiles of single tif ls images

```{r}
make_trace_df <- function(my_file_dir, msg = F){
  
  # read metadata
  y_px_size = read_tags(my_file_dir) %>%
    pluck("frame1", "y_resolution")
  # read image
  image <- my_file_dir %>%
    ijtiff::read_tif(msg = msg) 
  
  my_trace_df <- map_dfr(list(ch1 = 1, ch2 = 2), ~ image[, , .x, 1] %>% 
                     rowMeans(), .id = "Channels") %>% 
    pivot_longer(names_to = "Channel",
                 cols = contains("ch"),
                 values_to = "Fluorescence") %>%
    mutate(Channel = factor(Channel, c("ch2", "ch1")),
           y_px_size =  y_px_size,
           file_id = path_file(my_file_dir))
    
  
  rm(image, y_px_size)
  return(my_trace_df)
  
}

```

testing running with multicore
```{r}
my_read_tif_func <- function(my_file_path, msg = FALSE){
  ijtiff::read_tif(path = my_file_path, msg = msg)
}
my_read_tif_func(my_file_path = file_list[1])
```

```{r}

# future::plan(multisession, workers = 7)
future::plan(multicore)
tictoc::tic()
map(file_list, my_read_tif_func)
# future_map(file_list, my_read_tif_func)
tictoc::toc()
```


profiling

```{r}
profvis::profvis({
  y_px_size = read_tags(file_list[1]) %>% 
    pluck("frame1", "y_resolution")
  
  my_trace_df <- file_list[1] %>%
    ijtiff::read_tif(msg = F) %>%
    `[` ( , , 1, 1) %>%
    rowMeans() %>%
    dplyr::tibble(Fluorescence = .)
    # dplyr::tibble(Time = 1:length(.) * y_px_size / 1000, # set the time in seconds
    #        Fluorescence = .)
})


```



```{r}
file_list <- path_to_file2 %>% 
list.files(full.names = TRUE, pattern = "[0-9]_BG.tif$", recursive = TRUE) #%>% 

  
```


# make plotly plot

```{r}
make_plotly_profile <- function(ls_profile_df, size = 4){
  {ls_profile_df %>% 
      ggplot2::ggplot(aes(x = Time, 
                          y = Fluorescence)) +
      ggplot2::geom_line(size = size) + 
      ggplot2::facet_grid(Channel~ .)} %>% 
    ggplotly()
    
}
```


# extract metadata form a single tif file -> updated (remove warning cuased by setnames function) --> deprecated
deprecated

```{r}

# extract_metadata_tif <- function(file_dir, meta_data = "y_resolution"){
#   
#   if(meta_data == "all"){
#     metadata_df <- read_tags(file_dir, frames = "all") %>% 
#       pluck(pluck("frame1"))
#     
#   }else{
#     metadata_df <- meta_data %>%
#       map_dfc(~read_tags(file_dir, frames = "all") %>% 
#                 pluck(pluck("frame1"))) %>% 
#       select(all_of(meta_data))
#   }
# 
#   return(metadata_df)
# 
# }
# 
# 
# # file_list[1] %>% 
# path_to_file2 %>% 
#   
#   # read_tags( frames = "all")
#   # extract_metadata_tif()
#   # make_trace_df()
#   multiple_ls_profile %>% 
#   make_plotly_profile()
```

# create df profiles from multiples tif ls images concatenated -> deprecated for map_function

```{r}
# multiple_ls_profile <- function(my_dir){
#   #list the tif files in the provided directory
#   my_ls_file_list <- my_dir %>% 
#     fs::dir_ls(regexp = "[0-9]{4,4}_BG.tif$")
# 
#   # create df of files metadata
#   metadata <- my_ls_file_list %>% 
#     map_dfr(~extract_metadata_tif(.x, 
#                                   meta_data =  c("y_resolution")), 
#             .id = "file_id")
#   
#   full_ls_df <- my_ls_file_list %>% 
#     map_dfr(make_trace_df, .id = "file_id") %>% 
#     left_join(metadata, by = "file_id") %>% 
#     mutate(file_id = str_sub(file_id, start = -24)) %>% 
#     mutate(Time = 1:length(Fluorescence) * y_resolution / 1000) %>% #set in sec the time
#     select(-y_resolution)
#   
#   rm(my_ls_file_list, metadata)
#   
#   return(full_ls_df)
# }



# future::plan(multisession, workers = 7)
# future::plan(multicore)
# 
# multiple_ls_profile_parall <- function(my_dir){
#   
#   #list the tif files in the provided directory
#   my_ls_file_list <- my_dir %>% 
#     fs::dir_ls(regexp = "[0-9]{4,4}_BG.tif$")
# 
#   # create df of files metadata
#   metadata <- my_ls_file_list %>% 
#     furrr::future_map_dfr(~extract_metadata_tif(.x, 
#                                   meta_data =  c("y_resolution")), 
#             .id = "file_id")
#   
#   full_ls_df <- my_ls_file_list %>% 
#     furrr::future_map_dfr(make_trace_df, .id = "file_id") %>% 
#     left_join(metadata, by = "file_id") %>% 
#     mutate(file_id = str_sub(file_id, start = -24)) %>% 
#     mutate(Time = 1:length(Time) * y_resolution / 1000) %>% #set in sec the time
#     select(-y_resolution)
#   
#   rm(my_ls_file_list, metadata)
#   
#   return(full_ls_df)
# }
```




```{r}
clean_data_func <- function(raw_pooled_LS_df){
  raw_pooled_LS_df %>%
    # mutate(file_id = str_sub(file_id, start = -24)) %>% 
    mutate(Time = 1:length(Fluorescence) * y_px_size / 1000) %>% #set in sec the time
    select(-y_px_size)
}
```



```{r}
path_to_file2 %>% 
# list.files(full.names = TRUE, pattern = "[0-9]_BG.tif$", recursive = TRUE) %>%
  fs::dir_ls(regexp = "[0-9]{4,4}_BG.tif$") %>% 
  # str
  map_dfr(~make_trace_df(.x)) #%>% 
  # distinct(file_id)
  
  clean_data_func %>% 
  make_plotly_profile
  # map_dfr(~extract_metadata_tif(.x, meta_data =  c("y_resolution")), 
  #         .id = "file_id")# %>% 
  str()
```

```{r}
path_to_file2 %>% 
# list.files(full.names = TRUE, pattern = "[0-9]_BG.tif$", recursive = TRUE) %>%
  fs::dir_ls(regexp = "[0-9]{4,4}_BG.tif$") %>%
  `[` (1) %>% 
  make_trace_df_test()


```


```{r}
path_to_file2 %>%
  fs::dir_ls(regexp = "[0-9]{4,4}_BG.tif$") %>%
  # `[` (1) %>% 
  map_dfr(~make_trace_df_test(.x)) %>% 
  clean_data_func() %>% 
  # str
  make_plotly_profile(size = 0.2)
```

